---
title: "Live Assignment 10"
author: "Chris Donlan"
date: "November 11, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This is an analysis for New York Times home page ad click through rates. The data represents one simulated days’ worth of ads during May 2012. Each row represents a user. 

The raw data contains the following fields:
- Age
- Gender (0 = female and 1 = male)
- Number of Impressions
- Number of Clicks
- Whether user was logged in

Data was downloaded from:
http://stat.columbia.edu/~rachel/datasets/nyt1.csv.

The following libraries were used.
```{r}
library("ggplot2")
library("doBy")
```

Load the CSV file into a dataframe.
```{r}
#Read in data
nyt <- read.table("nyt1.csv",header=TRUE, ",")
class(data)
```

Use the cut function to categorize the users into various age categories.
```{r}
#Catagorize by age
bins <- c(-Inf,0,18,24,34,44,54,64,Inf)
nyt$AgeGroup = cut(nyt$Age,bins)
```

Remove observations were no ad impressions were made.
```{r}
#Subset data where Impressions > 0
ImpSub = subset(nyt, Impressions > 0)
```

Create new variable, click through rate(CTR), which is simply clicks divided by number of impressions.
```{r}
#Create click through rate variable
ImpSub$CTR = ImpSub$Clicks/ImpSub$Impressions
head(ImpSub, 100)
```

Plot histogram of impression's distribution.
```{r}
#plot distribution of CTR
ggplot(subset(ImpSub,CTR>0), aes(x=CTR, fill=AgeGroup)) + geom_histogram(binwidth = .05)
```

Plot histogram of CTR's distribution.
```{r}
#plot distribution of CTR
ggplot(subset(ImpSub,CTR>0), aes(x=CTR, fill=AgeGroup)) +geom_histogram(binwidth = .05)
```

Create new CTR group variable.
```{r}
ctrbins <- c(-Inf,0.2,0.4,0.6,0.8,Inf)
ImpSub$CTRGroup = cut(ImpSub$CTR,ctrbins)
```

Output summary stats.
```{r}
#Get mean of age
mean(ImpSub$Age)

#Get mean of Impressions
mean(ImpSub$Impressions)

#Get mean of CTR
mean(ImpSub$CTR)

#Percentage of Males and Femals
cbind( Freq=table(ImpSub$Gender), relative=100*prop.table(table(ImpSub$Gender)))

#Percentage of Signed in
cbind( Freq=table(ImpSub$Signed_In), relative=100*prop.table(table(ImpSub$Signed_In)))
```

Output summary by AgeGroup variable.
```{r}
#Get means of Impressions by Age group
summaryBy(Impressions~AgeGroup,data=ImpSub,FUN=c(mean))

#Get means of CTR by Age group
summaryBy(CTR~AgeGroup,data=ImpSub,FUN=c(mean))

#Get means of Gender by Age group
summaryBy(Gender~AgeGroup,data=ImpSub,FUN=c(mean))

#Get means of Signed_In by Age group
summaryBy(Signed_In~AgeGroup,data=ImpSub,FUN=c(mean))
```

Create new table based on CTRGroup and AgeGroup vectors.
```{r}
CTRAgeGroup <- table(ImpSub$CTRGroup,ImpSub$AgeGroup)
```

Plot histogram of CTR's distribution.
```{r}
ggplot(subset(ImpSub,CTR>0), aes(x=CTR, fill=AgeGroup)) +
  geom_histogram(binwidth = .025)
```

Plot interesting density plot of CTR and AgeGroup.
```{r}
ggplot(subset(ImpSub,CTR>0), aes(x=CTR, fill=AgeGroup)) +
  geom_density()
```
